---
title: "Data"
author: "Koen Lucas"
date: "`r Sys.Date()`"
output: html_document
---

# Data and methods

```{=html}
<style>
body {
text-align: justify}
</style>
```
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}

library(knitr)
library(formatR)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```

## Dependent variables

Originally, the data consisted of all scholars employed the sociology and political science departments of all universities in the Netherlands. The data on author publications have been webscraped from OpenAlex, a database cataloging scholar information. This contained both data on the ego characteristics as well as data on the publications of each individual scholar. To answer the research questions, in this paper data from four different sociology departments at four different universities (Radboud University, Utrecht University, University of Amsterdam, and Groningen University) in 2024 has been used (N = 234). Additional ego-level data has been added to this data, a detailed description on the collection of these variables is presented below. The publication data has been used to create two seperate waves of publication networks, wave 1 ranging from 2015 to 2019, and wave 2 ranging from 2020 to 2024. The collaboration networks were created by co-authorship ties, meaning that authors who have published together have a tie between each other. These ties are directed, the first author of a publication sends a tie to the co-authors. The underlying assumption is that the first author instigated the collaboration. In the context of cumulative advantage, this means that a scholar with a lot of indegrees (receiving ties) indicates that a lot of other authors want to collaborate with that scholar. A scholars' amount of indegrees will be one of the ways in which the prestige of a scholar is measured.

## Independent variables

### H-index

Another way in which the prestige of scholars is measured is through the h-index. This bibliometric is defined as the maximum value of *h* such that the scholar has published at least *h* works that have been cited *h* amount of times. The data for the H-index is similarly webscraped from OpenAlex. Due to anomalies in the OpenAlex database, some H-indices of authors do not correspond with the authors' real h-indices. These anomalies should be taken into account when interpreting the results.

### Career age

The author's career age has been calculated by determining the first year author's have published. Again, due to anomalies in the OpenAlex database some very unlikely outliers presented themselves in the data. To counter this, the first publication of an author was omitted in the calculation of career age and than a mean score of all publication years was calculated. The first publication year was than determined by looking at the minimum year within the range of the mean score - 25 years. This way the first publication years are not necessary correctly estimated, however these differences are small enough that they will likely not impact the results. Ultimately, the career age has been calculated by subtracting the first publication year from 2024. This way the higher the career age, the longer a scholar is publishing.

## descriptives

```{r clean workspace, include = FALSE}

rm(list = ls())

```

```{r load functions, include=FALSE}
rm(list = ls())


fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}


```

```{r load packages, include=FALSE}

packages <- c("tidyverse", 
              "scholar", 
              "RSiena", 
              "RsienaTwoStep", 
              "igraph")

fpackage.check(packages)
```

```{r load data, include=FALSE}

fulldata <- fload("./Data/full_data.Rdata")

df_ego <- fload("./Data/df_ego.Rdata")
  
df_works <- fload("./Data/df_works.Rdata")

```

```{r}

summary(df_ego$h_index)

summary(df_ego$career_age)

```
