---
title: "Results - descriptives"
author: "Koen Lucas"
date: "`r Sys.Date()`"
output: html_document
---

# Results - descriptives

```{=html}
<style>
body {
text-align: justify}
</style>
```
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}

library(knitr)
library(formatR)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```

```{r clean workspace, include = FALSE}

rm(list = ls())

```

```{r load functions, include=FALSE}

fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
    ifelse(!dir.exists("data"), dir.create("data"), FALSE)
    ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
    if (is.null(file))
        file = deparse(substitute(x))
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, file, "_", datename, ".rda", sep = "")
    save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
    load(filename)
    get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}


```

```{r load packages, include=FALSE}

packages <- c("tidyverse", 
              "scholar", 
              "RSiena", 
              "RsienaTwoStep", 
              "igraph",
              "poweRlaw",
              "ggraph")

fpackage.check(packages)

```

```{r load data, include=FALSE}

fulldata <- fload("./Data/full_data.Rdata")

df_ego <- fload("./Data/df_ego.Rdata")
  
df_works <- fload("./Data/df_works.Rdata")

```

```{r create graph objects, include=FALSE}

# wave 1
network_w1 <- igraph::graph_from_adjacency_matrix(
  fulldata$nets[1,,],
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

wave1 <- simplify(network_w1)

# wave 2
network_w2 <- igraph::graph_from_adjacency_matrix(
  fulldata$nets[2,,],
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

wave2 <- simplify(network_w2)

                  
```

## descriptive statistics

### Wave 1

```{r descriptive stats wave 1}
# number of nodes
# vcount(network_w1) # 234

# number of edges
ecount(network_w1)

### wave 1
# dyad-census
igraph::dyad_census(network_w1)

# triad-census
igraph::triad_census(network_w1)

# edge density
igraph::edge_density(network_w1)

```

The networks consist of 234 scholars. In wave 1 there are 145 edges, consisting of 19 reciprocated ties and 107 asymmetric ties. The edge density is 0,003, indicating that the total number of edges can be interpreted as relatively low compared to the total possible number of edges. Looking at the triadic relations, there is only one complete triad. A triad with no relations between each other (003) appears the most in this network.


### Wave 2

```{r descriptive stats wave 2}

### wave 2

#number of edges
ecount(network_w2) 
# dyad-census
igraph::dyad_census(network_w2)

# triad-census
igraph::triad_census(network_w2)

# edge density
igraph::edge_density(network_w2)

```

In wave 2 there are 258, which is a relatively steep increase compared to wave 1. The network consists of 30 reciprocated ties and 198 assymetric ties. The edge density is 0,005 and is only slightly higher than in wave 1, thus meaning that the number of edges is low compared to all posible edges within the network. Furthermore, inspecting the triadic relations, the number of complete triads increased from 1 to 2. The 003 triad (no relations between the three nodes) still occurs the most. 

### Transitivity

```{r transitivity}
# wave 1
igraph::transitivity(network_w1)
# wave 2
igraph::transitivity(network_w2)

```

The transitivity effect illustrates whether different co-authors of a scholar become co-authors. In wave 1 this index is 0,182. This means that a scholar who co-authors with two other scholars, the probability that these two scholars also become co-authors is 0,182. In wave 2 the transitivity index is 0,172, which is a slight (and probably insignificant) decrease compared to wave 1.

## Scale-free network - Wave 1

A network can be considered scale-free when the network's degree distribution follows a power-law (ref.):

$$P(k) \sim k^{-\gamma}$$

Where $P(k)$ is the probability, $k$ the degrees, and $\gamma$ is the scaling exponent. A distribution is considered scale-free when $\gamma$ is between 2 and 3.

In the case of preferential attachment in co-authorship this can be explained as the probability of a node having a certain number of co-authors decreases as the number of co-authors increases. In other words, when a node has a lot of co-authorship ties, it is less likely to find nodes with a similar high number of co-authorship ties. On the other hand, the probability of a node having only a small number of co-authorship ties is relatively high. Determining whether the networks exhibit a scale-free distribution is interesting when investigating a 'Matthew effect' in science. As preferential attachment can be seen as a mechanism driving scale-free networks, it shows that new connections are more likely to be formed with those who are already well-connected. This parallels an effect of cumulative advantage based on the indegrees of a node.

### Degree distribution wave 1 - including isolates

```{r wave 1 indegree distribution, echo=FALSE}
# wave 1
indegr_w1 <- degree(network_w1, mode = "in") # calculate indegrees

# create dataframe for indegrees
degree_table_w1 <- as.data.frame(table(indegr_w1))
colnames(degree_table_w1) <- c("Indegree", "Frequency")
degree_table_w1$Indegree <- as.numeric(as.character(degree_table_w1$Indegree))
# Create a complete indegree range
complete_indegree <- data.frame(Indegree = 0:max(degree_table_w1$Indegree))
degree_table_w1 <- merge(complete_indegree, degree_table_w1, by = "Indegree", all.x = TRUE)
# Calculate percentage for each indegree
degree_table_w1$Frequency[is.na(degree_table_w1$Frequency)] <- 0
degree_table_w1$Percentage <- (degree_table_w1$Frequency / sum(degree_table_w1$Frequency)) * 100


# indegree distribution - including isolates
ggplot(degree_table_w1, aes(x = Indegree, y = Percentage)) +
  geom_bar(stat = "identity", fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of indegrees - Wave 1 (percentage)", 
       x = "Indegrees", 
       y = "Percentage") +
  scale_x_continuous(breaks = seq(0, 15, 1)) + 
  scale_y_continuous(limits = c(0, max(degree_table_w1$Percentage) + 5)) +
  theme_minimal()

```

The indegree distribution above show a right-skewed distribution, which would be expected in a scale-free network. A lot of nodes of have no or only a few indegrees, while a small number of nodes have a lot of indegrees.

### Indegree distribution wave 1 - excluding isolates

```{r wave 1 degree distribution excluding isolates, echo=FALSE}
# filter out isolates
degree_table_w1_x <- degree_table_w1[degree_table_w1$Indegree > 0, ]
degree_table_w1_x$Percentage <- (degree_table_w1_x$Frequency / sum(degree_table_w1_x$Frequency)) * 100

# indegree distribution - excluding isolates
ggplot(degree_table_w1_x, aes(x = Indegree, y = Percentage)) +
  geom_bar(stat = "identity", fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of indegrees - Wave 1 (percentage)", 
       x = "Indegrees", 
       y = "Percentage") +
  scale_x_continuous(breaks = seq(1, 15, 1)) + 
  scale_y_continuous(limits = c(0, max(degree_table_w1$Percentage) + 5)) +
  theme_minimal()
```

### Estimating the scaling exponent $\gamma$

To estimate the $\gamma$ parameter isolates have to be disregarded. The indegree distribution excluding isolates shown above still shows a right-skewed distribution. The distribution is still in line with what is expected for a scale-free network. The $\gamma$ can be estimated using the R-package 'poweRlaw'. The $\gamma$ is estimated at roughly 4,82 (see below). As this value is not between 2 and 3 the network does not exhibits scale-free characteristics and, thus, can likely not be interpreted as such. Another property of a power-law distribution is that it looks like a straight line when plotted in a log-log plot (a plot in which both the x-axis and y-axis is represented using a logarithmic scale). This plot can be observed below and does actually present a straight line. However, this is due to the nature of plotting the powerlaw in a log-log plot. It can however be observed that the steep slope of this line indicates a more uniform indegree distribution. Altogether, in wave 1 there is likely not yet a preferential attachment mechanism in place. This is, however, likely to be the case due to the large amount of isolates in wave 1 due to a lot of the scholars not being active in wave 1, making it hard to distinguish any distinct 'hubs' of co-authorship in this timepoint.

```{r estimate powerlaw}

degree_df_w1 <- as.data.frame(table(indegr_w1))
degree_df_w1$indegr_w1 <- as.numeric(as.character(degree_df_w1$indegr_w1))

degree_df_w1 <- degree_df_w1[degree_df_w1$indegr_w1 > 0, ] # exclude isolates

pl <- displ$new(degree_df_w1$indegr_w1) # fit power law to distribution

estimate_w1 <- estimate_xmin(pl)
pl$setXmin(estimate_w1)

estimate <- estimate_xmin(pl)
pl$setXmin(estimate)

gamma <- pl$pars
gamma

```

```{r log log graph, echo=FALSE}

clean_data <- degree_table_w1_x %>% 
  filter(Frequency > 0)

log_fit <- lm(log(Frequency) ~ log(Indegree), data = clean_data)

ggplot(clean_data, aes(x = Indegree, y = Frequency)) +
  geom_point() + 
  labs(title = "Log-Log plot of indegree distribution - Wave 1", 
       x = "Indegrees (log-scale)", 
       y = "Frequencies (log-scale") +
  geom_smooth(method = "lm", color =  "blue", se = FALSE) + 
  scale_x_log10() + 
  scale_y_log10() +
  geom_curve(x = 7, y = 19, xend = 5, yend = 13,
             arrow = arrow(length = unit(0.5, "inches")), size = 1,
             color = "black", curvature = 0.0) +
     annotate("text", x = 6, y = 20, label = "the steeper slope \n suggests a more uniform \n degree distribution", size = 4) +
  theme_minimal()


```

## Scale-free network - Wave 2

### Degree distribution wave 2 - including isolates

```{r wave 2 indegree distribution, echo=FALSE}
# wave 2
indegr_w2 <- degree(network_w2, mode = "in") # calculate indegrees

# create dataframe for indegrees
degree_table_w2 <- as.data.frame(table(indegr_w2))
colnames(degree_table_w2) <- c("Indegree", "Frequency")
degree_table_w2$Indegree <- as.numeric(as.character(degree_table_w2$Indegree))
# Create a complete indegree range
complete_indegree <- data.frame(Indegree = 0:max(degree_table_w2$Indegree))
degree_table_w2 <- merge(complete_indegree, degree_table_w2, by = "Indegree", all.x = TRUE)
# Calculate percentage for each indegree
degree_table_w2$Frequency[is.na(degree_table_w2$Frequency)] <- 0
degree_table_w2$Percentage <- (degree_table_w2$Frequency / sum(degree_table_w2$Frequency)) * 100


# indegree distribution - including isolates
ggplot(degree_table_w2, aes(x = Indegree, y = Percentage)) +
  geom_bar(stat = "identity", fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of indegrees - Wave 2 (percentage)", 
       x = "Indegrees", 
       y = "Percentage") +
  scale_x_continuous(breaks = seq(0, 15, 1)) + 
  scale_y_continuous(limits = c(0, max(degree_table_w2$Percentage) + 5)) +
  theme_minimal()

```

### Indegree distribution wave 2 - excluding isolates

The indegree distribution above show a right-skewed distribution, which would be expected in a scale-free network. A lot of nodes of have no or only a few indegrees, while a small number of nodes have a lot of indegrees.

```{r wave 2 degree distribution excluding isolates, echo=FALSE}
# filter out isolates
degree_table_w2_x <- degree_table_w2[degree_table_w2$Indegree > 0, ]
degree_table_w2_x$Percentage <- (degree_table_w2_x$Frequency / sum(degree_table_w2_x$Frequency)) * 100

# indegree distribution - excluding isolates
ggplot(degree_table_w2_x, aes(x = Indegree, y = Percentage)) +
  geom_bar(stat = "identity", fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of indegrees - Wave 2 (percentage)", 
       x = "Indegrees", 
       y = "Percentage") +
  scale_x_continuous(breaks = seq(1, 15, 1)) + 
  scale_y_continuous(limits = c(0, max(degree_table_w2$Percentage) + 5)) +
  theme_minimal()
```

### Estimating the scaling exponent $\gamma$

The indegree distribution excluding isolates shown above still shows a right-skewed distribution. The distribution is still in line with what is expected for a scale-free network. The $\gamma$ is again estimated using the R-package 'poweRlaw'. The $\gamma$ is estimated at roughly 2,75 (see below). As this value is between 2 and 3 the network exhibits scale-free characteristics and can likely be interpreted as such. Below, in the log-log plot a straight line can be observed, in line with the characteristics of a power law distribution. The slope of this line more evidently indicates the presence of hubs, as one would expect in a scale-free network. Altogether, this would suggest a likely preferential attachment mechanism at play in the network at timepoint 2, meaning that already established authors with a lot of indegrees are more attractive to other authors than authors with less indegrees.

```{r estimate powerlaw wave 2}

degree_df_w2 <- as.data.frame(table(indegr_w2))
degree_df_w2$indegr_w2 <- as.numeric(as.character(degree_df_w2$indegr_w2))

degree_df_w2 <- degree_df_w2[degree_df_w2$indegr_w2 > 0, ] # exclude isolates

pl <- displ$new(degree_df_w2$indegr_w2) # fit power law to distribution

estimate_w2 <- estimate_xmin(pl)
pl$setXmin(estimate_w2)

estimate <- estimate_xmin(pl)
pl$setXmin(estimate)

gamma <- pl$pars
gamma

```

```{r log log graph wave 2, echo=FALSE}

clean_data <- degree_table_w2_x %>% 
  filter(Frequency > 0)

log_fit <- lm(log(Frequency) ~ log(Indegree), data = clean_data)

ggplot(clean_data, aes(x = Indegree, y = Frequency)) +
  geom_point() + 
  labs(title = "Log-Log plot of indegree distribution - Wave 2", 
       x = "Indegrees (log-scale)", 
       y = "Frequencies (log-scale)") +
  geom_smooth(method = "lm", color =  "blue", se = FALSE) + 
  scale_x_log10() + 
  scale_y_log10() +
  geom_curve(x = 7, y = 19, xend = 5, yend = 13,
             arrow = arrow(length = unit(0.5, "inches")), size = 1,
             color = "black", curvature = 0.0) +
     annotate("text", x = 7, y = 24, label = "the more gradual slope \n suggests the existence of \n a few hubs in the network", size = 4) +
  theme_minimal()


```


## Network visualisation

```{r clean workspace 2, include=FALSE}

rm(list = setdiff(ls(), c("fulldata", "df_ego", "df_works")))

```

```{r creating network objects, include=FALSE}

# wave 1
network_w1 <- igraph::graph_from_adjacency_matrix(
  fulldata$nets[1,,],
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

wave1 <- simplify(network_w1)


# wave 2
network_w2 <- igraph::graph_from_adjacency_matrix(
  fulldata$nets[2,,],
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

wave2 <- simplify(network_w2)

```

```{r initial plots, warning=FALSE, echo=FALSE, fig.show="hold", out.width="50%"}

plot(wave1,
     vertex.label = NA,
     vertex.size = 7,
     edge.curved = 0.2,
     edge.arrow.size = 0.1,
     main = "Network at wave 1")

plot(wave2,
     vertex.label = NA,
     vertex.size = 7,
     edge.curved = 0.2,
     edge.arrow.size = 0.1,
     main = "Network at wave 2")

indegr_w1 <- degree(wave1, mode = "in")
indegr_w2 <- degree(wave2, mode = "in")

isolates_w1 <- V(wave1)[degree(wave1, mode = "all") == 0]

noisolates_w1 <- delete_vertices(wave1, isolates_w1)

plot(noisolates_w1,
     vertex.label = NA,
     vertex.size = 10,
     vertex.color = "blue",
     vertex.frame.color = "black",
     edge.curved = 0.2,
     edge.arrow.size = 0.4,
     edge.color = "gray",
     edge.width = 0.3,
     main = "Network at wave 1 without isolates")


isolates_w2 <- V(wave2)[degree(wave2, mode = "all") == 0]

noisolates_w2 <- delete_vertices(wave2, isolates_w2)

plot(noisolates_w1,
     vertex.label = NA,
     vertex.size = 10,
     vertex.color = "blue",
     vertex.frame.color = "black",
     edge.curved = 0.2,
     edge.arrow.size = 0.4,
     edge.color = "gray",
     edge.width = 0.3,
     main = "Network at wave 2 without isolates")

```

Above, plots of both waves are presented, both with and without isolates. These plots show the networks before tampering with shape, size and position of the nodes. Furthermore, the plots show that the number of co-authorship ties has increased between timepoint 1 and timepoint 2.

### Plots by H-index and indegrees

```{r pretty plot wave 1, echo=FALSE}

### wave 1

indegr_w1 <- degree(wave1, mode = "in")

# assign h-index to scholar
V(wave1)$h_index <- df_ego$h_index
V(wave1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete.vertices(wave1, V(wave1)[degree(wave1) == 0])

#set size of plot
options(repr.plot.width = 20, repr.plot.height = 20)

#plot wave 1
ggraph(noisolates_w1,
       layout = "fr") +
  geom_edge_link(color = "gray", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index)) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "lightblue", high = "blue") + 
  theme_void() +
  labs(title = "Network wave 1: no isolates, node size based on indegrees & colour based on H-index")



```

```{r pretty plot wave 2, echo=FALSE}

### wave 2

indegr_w2 <- degree(wave2, mode = "in")

# assign h-index to scholar
V(wave2)$h_index <- df_ego$h_index
V(wave2)$indegree <- indegr_w2

#remove isolates
noisolates_w2 <- delete.vertices(wave2, V(wave2)[degree(wave2) == 0])

#set size of plot
options(repr.plot.width = 20, repr.plot.height = 20)

#plot wave 2
ggraph(noisolates_w2,
       layout = "fr") +
  geom_edge_link(color = "gray", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index)) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "lightblue", high = "blue") + 
  theme_void() +
  labs(title = "Network wave 2: no isolates, node size based on indegrees & colour based on H-index")

```
